|

### 2022-06-14 draft-1.Rmd
Quantum finaglery

output:
  bookdown::word_document2:
    number_sections: false
    reference_docx: template.docx
lot: true
lof: true
toc: false

@@

l <- readRDS("data/lagrange.Rds")
library(tidyverse)
library(texreg)
library(spatialreg)
source("R/extract.R")
model_list <- readr::read_rds("model_list.Rds")
```

@@

Proximity to greenspace is a potential determinant on an individual’s mental health [@nutsford2013; @ekkel2017; @collins2020; @sakar2018; @jiang2021]. As a low-cost mental health intervention, greenspace provides restorative experiences, encourages social cohesion, reduces pollution, and offers opportunities for physical activity [@lachowecyz2013; @wang2021]. To date, most greenspace research has focused on the greenspace mental health relationship in urban areas, with less attention focused on rural communities [@collins2020]. Within studies that have considered the greenspace mental health relationship in rural areas, evidence is mixed, with some studies finding greenspace benefits mental health similarly in rural areas as compared to urban areas [@verheji2008; @alcock2015]. Other research suggests that the rural greenspace mental health relationship differs from the urban relationship [@jiang2021], with private greenspaces — including yards, agricultural fields, and general “countryside greenness” — playing an important role in the rural greenspace mental health relationship [@ekkel2017]. As such, further investigation into the rural greenspace mental health relationship is needed, specifically with regards to public greenspace quality, in addition to greenspace quantity — i.e., available area within a greenspace.

@@

```{r extent, fig.width = 4.5, fig.cap = "Extent of ZIP codes (dark gray) within Western NC (light gray)"}
knitr::include_graphics("fig/brownExtent.png", dpi = 600)
```

@@

knitr::kable(moran,
             col.names = c("Variable", "Moran's I", "Expected", "Variance", "SD", "p value"),
             caption = "Calculated statistics for Moran’s I across predictor and response variables")

>>>>

output:
  officedown::rdocx_document:
    number_sections: false
    reference_docx: template.docx
    tables:
      style: stat_table
    plots:
      align: center
    page_size:
      width: 8.5
      heigh: 11
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1

lot: true
lof: true
toc: false

@@

l <- readRDS("data/lagrange.Rds")
library(officedown)
library(tidyverse)
library(texreg)
library(spatialreg)
source("R/extract.R")
model_list <- readr::read_rds("model_list.Rds")
```

@@

Proximity to greenspace is a potential determinant on an individual’s mental health [@nutsford2013; @ekkel2017; @collins2020; @sakar2018; @jiang2021]. As a low-cost mental health intervention, greenspace provides restorative experiences, encourages social cohesion, reduces pollution, and offers opportunities for physical activity [@lachowycz2013; @wang2021]. To date, most greenspace research has focused on the greenspace mental health relationship in urban areas, with less attention focused on rural communities [@collins2020]. Within studies that have considered the greenspace mental health relationship in rural areas, evidence is mixed, with some studies finding greenspace benefits mental health similarly in rural areas as compared to urban areas [@verheji2008; @alcock2015]. Other research suggests that the rural greenspace mental health relationship differs from the urban relationship [@jiang2021], with private greenspaces — including yards, agricultural fields, and general “countryside greenness” — playing an important role in the rural greenspace mental health relationship [@ekkel2017]. As such, further investigation into the rural greenspace mental health relationship is needed, specifically with regards to public greenspace quality, in addition to greenspace quantity — i.e., available area within a greenspace.

@@

```{r extent, fig.width = 4.5, fig.cap = "Extent of ZIP codes (dark gray) within Western NC (light gray)"}
knitr::include_graphics("fig/brownExtent.png")
```

@@

knitr::kable(moran,
             format = "latex",
             col.names = c("Variable", "Moran's I", "Expected", "Variance", "SD", "p value"),
             caption = "Calculated statistics for Moran’s I across predictor and response variables")

### 2022-06-14 references.Rmd
Quantum finaglery

---
output: word_document
bibliography: bibliography.bib
csl: seg.csl
nocite: |
  @nutsford2013; @ekkel2017; @collins2020; @sakar2018; @jiang2021; @lachowcyz2013; @wang2021; @collins2020; @verheji2008; @vandillen2012; @wood2017; @wheeler2015 @mears2019; @houlden2019; @mears2019a; @mccal-hosenfeld2014; @cdc2022; @feng2017; @zhang2017; @beyer2014; @mceachen2015; @shin2020; @johnson2018; @feng2020; @thetrustforpublicland2021; @openstreetmap2022; @runkle2022; @slawsky2022; @usgs2019; @wood2018; @browning2018; @hoffiman2017; @rigolon2018; @acs2018; @anselin2009; @legendre1993; @rstudioteam2022; @rcoreteam2022; @beyer2014; @houlden2019; @wang2021; @shin2020; @johnson2018; @xie2020; @feng2020; @chum2015; @astell-burt2020; @feng2017; @mahec; @alcock2015; @devries2020
---

>>>>

---
output: word_document
bibliography: bibliography.bib
csl: seg.csl
# nocite: |

---

[@nutsford2013; @ekkel2017; @collins2020; @sakar2018; @jiang2021; @lachowcyz2013; @wang2021; @verheij2008; @vandillen2012; @wood2017; @wheeler2015 @mears2019; @houlden2019; @mears2019a;  @mccal-hosenfeld2014; @cdc2022; @feng2017; @zhang2017; @beyer2014; @mceachen2015; @shin2020; @johnson2018; @feng2020; @thetrustforpublicland2021;  @openstreetmap2022; @runkle2022; @slawsky2022; @usgs2019; @wood2018;  @browning2018; @hoffimann2017; @rigolon2018; @acs2018; @anselin2008; @legendre1993; @rstudioteam2022; @rcoreteam2022; @beyer2014; @houlden2019;  @wang2021; @shin2020; @johnson2018; @xie2020; @feng2020; @chum2015;  @astell-burt2020; @feng2017; @mahec; @alcock2015; @devries2020; @feng2017;  @gresenz2001; @reiss2013; @howell2008; @padgham2017; @sarkar2018]
